---
title: "Captura-recaptura"
author: "David Murillo"
format: html
---

::: panel-tabset

## Cargar paquete

```{r}
library(multimark)
```


[Referencia](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4662319/)

## Cargar base de datos

```{r}
data(bobcat)
head(bobcat)
tail(bobcat)
```

## Crear con covariable

```{r}
dummy <- rnorm(ncol(bobcat)) # some fake temporal covariates
Forest <- rnorm(ncol(bobcat))
Bird <- rpois(ncol(bobcat), 3)
Habitat <- rep(c("A", "B"), each = ncol(bobcat) / 2)

Covs <- data.frame(dummy = dummy,
                   Forest = Forest,
                   Habitat= Habitat)
```


## Procesar base de datos

```{r}
bobcatsetup <- processdata(Enc.Mat=bobcat,data.type= "never", covs = Covs)
```


## Ajustar Modelos



```{r}
bobcat1 <- multimarkClosed(mms=bobcatsetup,
                           mod.p=~1,
                           parms="all",
                           nchains=2,iter=45000,burnin=5000)

bobcat2 <- multimarkClosed(mms=bobcatsetup,
                                  mod.p=~dummy + Habitat,
                                  parms="all",
                           nchains=2,iter=45000,burnin=5000)

bobcat3 <- multimarkClosed(mms=bobcatsetup,
                           mod.p=~Forest + Habitat,
                           parms="all",
                           nchains=2,iter=45000,burnin=5000)

bobcat4 <- multimarkClosed(mms=bobcatsetup,
                           mod.p=~dummy + Forest,
                           parms="all",
                           nchains=2,iter=45000,burnin=5000)

bobcat5 <- multimarkClosed(mms=bobcatsetup,
                           mod.p=~Habitat,
                           parms="all",
                           nchains=2,iter=45000,burnin=5000)
```




                        




## Resultados 

summary(bobcat4$mcmc)
summary(bobcat5$mcmc)


> Posterior model probabilities (PMM) and abundance estimates for the bobcat data. 

> Summaries include posterior modes (N), 95% highest posterior density intervals (HPDI), effective sample sizes (ESS), and Gelman–Rubin–Brooks diagnostics (GRB) for N. Models for detection probability (p) included no effects (˜1), behavioral effects (˜c), time effects (˜time), and individual effects (˜h). Models for the conditional probability of a left‐ or right‐sided encounter (delta) included δ 1=δ 2 (˜1) and δ 1≠δ 2 (˜type)


:::

